DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Label mistakes

# Rename columns
CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentOpportunities"))

>>>>

# Rename columns
CPerceivedOpportunities <- plyr::rename(x = CPerceivedOpportunities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentOpportunities"))
